\myTitle

### 2024-05-14 tex/supplemental-figures.tex
Big overhaul just before I gave lab meeting about this

>>>>

%%%%%%%%%%%%%%%%%%%%%% 
\begin{figure}
\begin{center}
\includegraphics[width=0.7\textwidth]{images/minor-modes-crop.pdf}
\end{center}
\caption[STRUCTURE minor modes found by CLUMPAK]{\footnotesize At each value of $K$
for which a minor mode was found, these plots show them}
\label{fig:minor-modes}
\end{figure}
%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%% 
\begin{figure}
\begin{center}
\includegraphics[width=0.8\textwidth]{images/ass-table-80-crop.pdf}
\end{center}
\caption[Assignment table for fish with scaled likelihood $ > 0.8$]{\footnotesize Assignment table
like that in Fig.~\ref{fig:gsi}b in the paper, but constrained so that only fish assigning
to a reporting unit with scaled likelihood greater than 0.8 are included.}
\label{fig:eighty}
\end{figure}
%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%% 
\begin{figure}
\begin{center}
\includegraphics[width=0.8\textwidth]{images/rosa-gsi-table-crop.pdf}
\end{center}
\caption[Assignment table by RoSA genotype]{\footnotesize Assignment table
like that in Fig.~\ref{fig:gsi}b in the paper, but with numbers according to genotypes
at the RoSA}
\label{fig:rosa-gsi}
\end{figure}
%%%%%%%%%%%%%%%%%%%%
